---
title: "R Notebook"
author: "Adriana Sham Luo"
date: "10/23/2019"
output:
  word_document: default
  html_document:
    df_print: paged
---

(1) Import all files to R. Use package readr. When reading English 2006 2012 All.csv, you can specify na() option in read csv() to define characters to interpreted as missing.
```{r}
library(magrittr)
pacman::p_load(dplyr)
rm(list = ls())
English_2006_2012_All = read.csv("English_2006_2012_All.csv", header = TRUE, sep = ",") 
e1 = na.omit(English_2006_2012_All)
str(e1)
e1 %<>%
  mutate(Mean.Scale.Score = as.numeric(Mean.Scale.Score)) %>%
  mutate(Num.Level.1 = as.numeric(Num.Level.1)) %>%
  mutate(Pct.Level.1 = as.numeric(Pct.Level.1 )) %>%
  mutate(Num.Level.2 = as.numeric(Num.Level.2)) %>%
  mutate(Pct.Level.2 = as.numeric(Pct.Level.2 )) %>%
  mutate(Num.Level.3 = as.numeric(Num.Level.3)) %>%
  mutate(Pct.Level.3 = as.numeric(Pct.Level.3)) %>%
  mutate(Num.Level.4 = as.numeric(Num.Level.4)) %>%
  mutate(Pct.Level.4 = as.numeric(Pct.Level.4)) %>%
  mutate(Num.Level.3.and.4 = as.numeric(Num.Level.3.and.4)) %>%
  mutate(Pct.Level.3.and.4 = as.numeric(Pct.Level.3.and.4))

str(e1)

English_2013_2017_All = read.csv("English_2013_2017_All.csv", header = TRUE, sep = ",", na.strings = "NA")
e2 = na.omit(English_2013_2017_All)

Math_2006_2012_All = read.csv("Math_2006_2012_All.csv", header = TRUE, sep = ",", na.strings = "NA")
m1 = na.omit(Math_2006_2012_All)

Math_2013_2017_All = read.csv("Math_2013_2017_All.csv", header = TRUE, sep = ",", na.strings = "NA")
m2 = na.omit(Math_2013_2017_All)

colnames(e1) = c("DBN", "Grade", "Year", "Demographic", "Number.Tested", "Mean.Scale.Score", "Num.Level.1", "Pct.Level.1", "Num.Level.2", "Pct.Level.2", "Num.Level.3", "Pct.Level.3", "Num.Level.4", "Pct.Level.4", "Num.Level.3.and.4", "Pct.Level.3.and.4")

colnames(e2) = c("DBN", "Grade", "Year", "Demographic", "Number.Tested", "Mean.Scale.Score", "Num.Level.1", "Pct.Level.1", "Num.Level.2", "Pct.Level.2", "Num.Level.3", "Pct.Level.3", "Num.Level.4", "Pct.Level.4", "Num.Level.3.and.4", "Pct.Level.3.and.4")

colnames(m1) = c("DBN", "Grade", "Year", "Demographic", "Number.Tested", "Mean.Scale.Score", "Num.Level.1", "Pct.Level.1", "Num.Level.2", "Pct.Level.2", "Num.Level.3", "Pct.Level.3", "Num.Level.4", "Pct.Level.4", "Num.Level.3.and.4", "Pct.Level.3.and.4")

colnames(m2) = c("DBN", "Grade", "Year", "Demographic", "Number.Tested", "Mean.Scale.Score", "Num.Level.1", "Pct.Level.1", "Num.Level.2", "Pct.Level.2", "Num.Level.3", "Pct.Level.3", "Num.Level.4", "Pct.Level.4", "Num.Level.3.and.4", "Pct.Level.3.and.4")
```

(2) Change the measurements of percent passing variables to ratios by dividing them by 100.
(3) Append the English score data sets and name it English 2006 2017 all. Similarly append the Math score data sets and name it Math 2006 2017 all.
```{r}
English_2006_2017_All = rbind(e1, e2)
English_2006_2017_All %<>%
  mutate(Pct.Level.1 = Pct.Level.1/100) %>%
  mutate(Pct.Level.2 = Pct.Level.2/100) %>%
  mutate(Pct.Level.3 = Pct.Level.3/100) %>%
  mutate(Pct.Level.4 = Pct.Level.4/100) %>%
  mutate(Pct.Level.3.and.4 = Pct.Level.3.and.4/100)


Math_2006_2017_All = rbind(m1, m2)
Math_2006_2017_All %<>%
  mutate(Pct.Level.1 = Pct.Level.1/100) %>%
  mutate(Pct.Level.2 = Pct.Level.2/100) %>%
  mutate(Pct.Level.3 = Pct.Level.3/100) %>%
  mutate(Pct.Level.4 = Pct.Level.4/100) %>%
  mutate(Pct.Level.3.and.4 = Pct.Level.3.and.4/100)
```

(4) Merge English 2006 2017 all and Math 2006 2017 all on DBN, Year and Grade. Name this data set ME 2006 2017 all.
```{r}
ME_2006_2017_all = merge(English_2006_2017_All, Math_2006_2017_All, by=c("DBN", "Grade", "Year"), all.x  = T, all.y = T, suffixes = c(".english",".math"))

rm(list=setdiff(ls(), "ME_2006_2017_all"))
```

(5) Generate a new string variable, borough, by slicing the third character in the DBN column in ME 2006 2017 all.
```{r}
ME_2006_2017_all %<>%
  mutate(borough = substr(DBN, 3,3)) %>%
  mutate(borough = as.factor(borough))
```

(6) Generate a table of descriptive statistics for ME 2006 2017 all. You can use package stargazer().
```{r}
stargazer::stargazer(ME_2006_2017_all, type = "text")
```

(7) Grouping by borough, year and grade, obtain mean, standard deviation, min and max of percent passing scores for both types of exam.
```{r}
ME_2006_2017_all = ME_2006_2017_all[complete.cases(ME_2006_2017_all), ]
ME_2006_2017_all %>%
  group_by(borough, Year, Grade) %>%
  summarize(mean_english = mean(Pct.Level.3.and.4.english), min_english= min(Pct.Level.3.and.4.english), max_english = max(Pct.Level.3.and.4.english), sd_english = sd(Pct.Level.3.and.4.english), mean_math = mean(Pct.Level.3.and.4.math), min_math= min(Pct.Level.3.and.4.math), max_math = max(Pct.Level.3.and.4.math), sd_math= sd(Pct.Level.3.and.4.math))
```

(8) Generate a new numeric variable, district, by slicing the first two characters in the DBN column in ME 2006 2017 all.
```{r}
ME_2006_2017_all %<>%
  mutate(district = substr(DBN, 1,2)) %>%
  mutate(district = as.numeric(district))
str(ME_2006_2017_all)
```

(9) Regress percent passing for English scores, on an intercept, year dummies, borough dummies and district dummies.
```{r}
year.f = factor(ME_2006_2017_all$Year)
# year_dummies = model.matrix(~year.f)
borough.f = factor(ME_2006_2017_all$borough)
# borough_dummies = model.matrix(~borough.f)
district.f = factor(ME_2006_2017_all$district)
# district_dummies = model.matrix(~district.f)

y_english = ME_2006_2017_all$Pct.Level.3.and.4.english
mod = lm(y_english ~ 1 + year.f + borough.f + district.f)
summary(mod)
```

(10) Regress percent passing for Math scores, on an intercept, year dummies, borough dum- mies and district dummies.
```{r}
y_math = ME_2006_2017_all$Pct.Level.3.and.4.math
mod2 = lm(y_math ~ 1 + year.f + borough.f + district.f)
summary(mod2)
```
